NumPy---Array Computation for Python

### 2020-01-09 body.tex
Typo

The first incarnation of NumPy was a package called Numeric, written in 1995
by Jim Hugunin, then completing his master's thesis at MIT.
Hugunin based his package on previous work by Jim Fulton,
then working at the US Geological Survey, and acknowledges
many others in his initial report of the package \cite{Hugunin-whitepaper}.
Later, Paul Dubois at Lawrence Livermore National Laboratory toke over the project
and funded the writing of the first
manual\footnote{https://conference.scipy.org/scipy2010/slides/travis\_oliphant\_keynote.pdf}
Numeric provided an array object in Python, written in C, and linking to
standard fast implementations of linear algebra.
% https://stackoverflow.com/questions/26948776/where-did-the-term-broadcasting-come-from/26950256
% https://mail.python.org/pipermail/matrix-sig/1995-November/000143.html
% May want to mention Yorick here (origin of broadcasting idea; it is mentioned later)
% https://aip.scitation.org/doi/pdf/10.1063/1.4823451 
% https://www.dyalog.com/uploads/documents/Papers/Arrays%20of%20Objects.pdf

>>>>

The first incarnation of NumPy was a package called Numeric, written in 1995
by Jim Hugunin, then completing his master's thesis at MIT.
Hugunin based his package on previous work by Jim Fulton,
then working at the US Geological Survey, and acknowledges
many others in his initial report of the package \cite{Hugunin-whitepaper}.
Later, Paul Dubois at Lawrence Livermore National Laboratory toke over the project
and funded the writing of the first
manual\footnote{https://conference.scipy.org/scipy2010/slides/travis\_oliphant\_keynote.pdf}.
Numeric provided an array object in Python, written in C, and linking to
standard fast implementations of linear algebra.
% https://stackoverflow.com/questions/26948776/where-did-the-term-broadcasting-come-from/26950256
% https://mail.python.org/pipermail/matrix-sig/1995-November/000143.html
% May want to mention Yorick here (origin of broadcasting idea; it is mentioned later)
% https://aip.scitation.org/doi/pdf/10.1063/1.4823451 
% https://www.dyalog.com/uploads/documents/Papers/Arrays%20of%20Objects.pdf
